### 2017-06-02 Manuscripts/cog-psych/cogpsych.tex
refining, PERFECTING, changes to the intro

The creation of new ideas is one of the most fascinating, important, and difficult human capabilities to study. Although we tend to focus on the most salient products of the processes underlying creative generation (e.g., scientific breakthroughs), every person is likely to have generated many novel concepts in ordinary life. Questions concerning the generation of novel concepts are typically addressed within research on creativity, which utilizes a diverse collection of empirical and theoretical approaches \citep[see][]{kaufman2010handbook}. However, due to the difficult nature of studying creative generation, this work infrequently employs computational methods to evaluate proposed processes and representations.

In this paper, we approach the problem of creativity in terms of

In particular, generating a member of a novel category can be considered as a `special case' application of existing category knowledge \cite{kemp2014taxonomy}: whereas research in categorization typically addresses how knowledge is used to classify items into known categories \citep[e.g.,][]{shepard1961learning,nosofsky1994comparing} or infer unobserved features of known category members \citep[see][]{markman2003category}. The generation of members of new categorires can be considered as a special case of such an inference

>>>>

The creation of new ideas is one of the most fascinating, important, and difficult human capabilities to study. Although we tend to focus on the most salient products of the processes underlying creative generation (e.g., scientific breakthroughs), every person is likely to have generated many novel concepts in ordinary life.

Questions concerning the generation of novel concepts are typically addressed within research on creativity, which utilizes a diverse collection of empirical and theoretical approaches \citep[see][]{kaufman2010handbook}.

However, due to the difficult nature of studying creative generation, this work infrequently employs computational methods to evaluate proposed processes and representations.

In this paper, we assume a different approach to studying the generation of novel concepts.

In particular, generating a member of a novel class can be considered a `special case' application of existing category knowledge \citep{kemp2014taxonomy,kurtz2015human}. Research in categorization typically focuses on classification \citep[predicting the category given feature information, see][]{shepard1961learning,nosofsky1994comparing} and inference \citep[predicting unobserved features given observed features and a category label, see][]{markman2003category}. Under this framing, the generation of new category members consists of inferring the {\em all} features given a novel category label. Thus, we can make progress in developing formal theories of creative generation by extending theories of categorization to the task of category generation.

 whereas research in categorization typically addresses how knowledge is used to classify items into known categories  or infer unobserved features of known category members \citep[see][]{markman2003category}. The generation of members of new categories can be considered as a special case of such an inference
